A Data-Driven Framework for Neural Field Modeling

### 2011-01-03 ltx/first_order_framework/response_to_reviews.tex

\emph{Gaussians have semi-compact support but Fourier basis functions are global functions. Gaussian can be easily extended to higher dimension (don't know about the Fourier basis functions), any orthonormal basis functions like Fourier basis functions simplify our equations, $\Gamma$ becomes identity matrix, but using Gaussian basis functions equations are in their generic form.}

\item In equation 29, what would a reasonable $v_c$ be for a real neuronal system (mammalian) given the number of neurons and scale of electrodes? I am concerned that it might be much higher than any of us wish to consider. One would perhaps be saved by the filter characteristics of brain (e.g. Phys. Rev. E 73, 051911 (2006)).

\item The two covariance inflation parameters in equation 41 make me cringe. How are we best to adjust these fudge factors?\\

\emph{Values for the two parameters in equation 41 along with the relevant references have been added to the manuscript.}

@@

\item I understand that the Mexican Hat bases are in this paper often a composite of $\theta_0$, $\theta_1$, and $\theta_2$, representing short range excitation, short range inhibition, and long range excitation. But many will be confused by this subtlety, and at times in the text the Mexican Hat basis is described as if it were a single function. I would show how the theta's sum to create the general spatial basis shape of the hat in figure 1, and go through the paper in order to clarify this issue.\\

\emph{This point is clarified by adding the connectivity kernel componets superimposed by the resulting Mexican Hat basis in Figure 1. of the manuscript.}

 \begin{figure*}[!ht]
 \begin{center}
 \includegraphics{./Graph/pdf/fig1.pdf} 
 \end{center}
 \caption{}
 \label{fig:Figure1}
 \end{figure*}

\item A few comments on how to adapt the smoother for real time implementation would be helpful. I presume that one would perform the smoothing during a training phase. But one would also wish to adapt in real time as observation or control scenarios progressed. A few words of perspective would be invaluable to help others translate the author's wisdom on this method to other applications.
\item Figure 4. Should the axes be indicated as spatial frequency rather than just Hz?\\

\emph{Axes of Figure 4. (and also Figure 5.) are now changed to spatial frequency. The unit of the spatial frequency within the text is changed to ?????}

\item Page 45, Appendix D, Par 1, line 6: should `transform of a n-' should be `transform of an n-' ? I am grammatically challenged perhaps.
\end{enumerate}

### 2011-01-03 ltx/first_order_framework/LaTeX_Manuscript.tex
minor comments

\subsection{Spatial Frequency Analysis}
The spectral analysis was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field. Fig.~\ref{fig:Figure4}(A) shows the spatial frequency of the neural field and Fig.~\ref{fig:Figure4}(B) shows the spatial frequency of the reconstructed neural field from the basis function decomposition. The cutoff frequency ($-3$~dB point) of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~Hz. From equation~\ref{eq:MinimumSensorDistance}, this yielded a maximum sensor separation of 2.08~mm. This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to mitigate problems associated with spatial aliasing of the dominant dynamics.

The spatial frequency of the observed field is shown in Fig.~\ref{fig:Figure5}(A). The cutoff frequency is $\boldsymbol{\nu}_{cy} \approx 0.2$~Hz ($-3$~dB point). The observation cutoff frequency is lower than the field cutoff due to the low-pass filtering effect of the sensors. The spatial frequency response of the sensors can be seen in Fig.~\ref{fig:Figure5}(B).

As described in Section~\ref{SpectralAnalysisSection}, the basis function configuration can be systematically chosen to account for the full spatial bandwidth from the observations, or alternatively, the configuration can be chosen to represent the neural field up to a specified bandwidth to limit the computational complexity of the estimation procedure. In the examples provided in this paper, the later option was chosen, where the neural field cutoff frequency was further reduced to $\boldsymbol{\nu}_{c\phi} = 0.12$~Hz. The band-limiting effect on the field reconstruction can be seen by comparing Fig.~\ref{fig:Figure4}(A) to Fig.~\ref{fig:Figure4}(B). This effect is due to the spatial frequency response of the basis functions, which is shown in Fig.~\ref{fig:Figure5}(C). Due to the slow roll-off in the frequency response of Gaussian basis functions an oversampling parameter of $\rho_{\phi} = 1.67$ was chosen. Given the spectral response of the basis functions, the over-sampling parameter, and the spatial domain an equally spaced grid of $9\times9$ basis functions was used to decompose the field, which resulted in $81$ states.

@@

	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cutoff frequency & Hz \\
	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & Hz$^2$\\

>>>>

\subsection{Spatial Frequency Analysis}
The spectral analysis was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field. Fig.~\ref{fig:Figure4}(A) shows the spatial frequency of the neural field and Fig.~\ref{fig:Figure4}(B) shows the spatial frequency of the reconstructed neural field from the basis function decomposition. The cutoff frequency ($-3$~dB point) of the neural field is \parham{$\boldsymbol{\nu}_c \approx 0.24$~Hz}. From equation~\ref{eq:MinimumSensorDistance}, this yielded a maximum sensor separation of 2.08~mm. This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to mitigate problems associated with spatial aliasing of the dominant dynamics.

The spatial frequency of the observed field is shown in Fig.~\ref{fig:Figure5}(A). The cutoff frequency is \parham{$\boldsymbol{\nu}_{cy} \approx 0.2$~Hz} ($-3$~dB point). The observation cutoff frequency is lower than the field cutoff due to the low-pass filtering effect of the sensors. The spatial frequency response of the sensors can be seen in Fig.~\ref{fig:Figure5}(B).

As described in Section~\ref{SpectralAnalysisSection}, the basis function configuration can be systematically chosen to account for the full spatial bandwidth from the observations, or alternatively, the configuration can be chosen to represent the neural field up to a specified bandwidth to limit the computational complexity of the estimation procedure. In the examples provided in this paper, the later option was chosen, where the neural field cutoff frequency was further reduced to \parham{$\boldsymbol{\nu}_{c\phi} = 0.12$~Hz}. The band-limiting effect on the field reconstruction can be seen by comparing Fig.~\ref{fig:Figure4}(A) to Fig.~\ref{fig:Figure4}(B). This effect is due to the spatial frequency response of the basis functions, which is shown in Fig.~\ref{fig:Figure5}(C). Due to the slow roll-off in the frequency response of Gaussian basis functions an oversampling parameter of $\rho_{\phi} = 1.67$ was chosen. Given the spectral response of the basis functions, the over-sampling parameter, and the spatial domain an equally spaced grid of $9\times9$ basis functions was used to decompose the field, which resulted in $81$ states.

@@

	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cutoff frequency & \parham{Hz} \\
	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & \parham{Hz}$^2$\\
